### 2022-01-06 content/31.tooling-table.tex
Alan's typo fixes and copy-editing
Signed-off-by: Stian Soiland-Reyes <stain@apache.org>
Typos fixed as in proof to IOS Press

		\textbf{ro-crate-excel} \citep{ro-crate-excel} & Data managers & JavaScript \\
		\multicolumn{4}{l}{\it Command-line tool to create/edit RO-Crates with spreadsheets} \\

@@

		\textbf{ONI express} \citep{arkisto-data-portal} & Repository managers & Platform & Beta \\
		\multicolumn{4}{l}{\it Platform for publishing data and documents stored in an OCFL repository via a web interface} \\

>>>>

		\textbf{ro-crate-excel} \citep{ro-crate-excel} & Data managers & JavaScript & Beta \\
		\multicolumn{4}{l}{\it Command-line tool to create/edit RO-Crates with spreadsheets} \\

@@

		\textbf{ONI express} \citep{arkisto-data-portal} & Repository managers & Platform & Beta \\
		\multicolumn{4}{l}{\it Platform for publishing data and documents stored in an OCFL repository via a Web interface} \\
